Domestic cooking and likelihood

### 2020-01-09 inst/cook.Rmd
clarification

Now, after the training we have two order observations: `1,2,3,4,5`
and `3,1,5,2,4`.  Thus player 1 comes first and second (after player
3) respectively.  The likelihood for the first would be

@@

and the likelihood for the second would be

>>>>

Now, after the training we have two order observations: `1,2,3,4,5`
and `3,1,5,2,4`.  Thus in the first observation, player 1 comes first
and in the second observation, player 1 comes second second (after
player 3).  The likelihood for the first observation would be

@@

and the likelihood for the second observation would be
